### 2018-02-22 Paper/jaccardbaetica.tex
change horn-morisita

@@

This paper aims to highlight the production dynamics in relation to a specific area within Roman Empire. We explore here the economic relationship between stamps and production centres.

@@

%%\subsection{Jaccard distance}
%%usar Jaccard disimilarity and similarity
%%
%The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity by calculating the presence of sets (CITAR). In our case, Jaccard distance was used to compute the mutual presence of traits in the amphora stamps but it does not consider the number of absences. A comparison was done with the distance of the workshops to identify whether there was an association between stamps and spatial distance amongst workshops.

%indicar si se usa en archaeology el jaccard distance

@@

As a complement of Jaccard distance, we use the statistical technique Morisita-Horn index. Unlike Jaccard distance, this method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity \citep{wolda_similarity_1981}. Morisita-Horn index can be expressed considering 0 as total presence of similarity of stamps and 1 a totally dissimilarity between stamps.

@@

\subsection{Jaccard distance}

Result of Jaccard distance can be The coefficients range from x to x.

The dendrogram shown in Fig. Bla bla was obtained with the Jaccard distance measure. The dendrogram suggests

>>>>

\begin{frontmatter}

\begin{abstract}

The aim of this study is to detect the patterns of olive oil production that link amphora workshops and amphoric stamps. Roman provinces such as Baetica became important production and distribution centers during the Roman Empire. However, it remains under debate how this province was organized and whether it is possible to identify patterns in the olive oil market.

Our case of study has been focused on the production processes located in Baetica province (currently Andalusia) from 1st to 3rd AD. In particular, we want to explore economic dynamics that include the production and distribution of olive oil trade. Amphoric stamps are used to identify the presence of different producer groups that might share similar stamps. To achieve this goal, we analyse a set of stamps from different workshops in Baetica province in order to detect a relation between the distribution of amphoric stamps and the economic structure in this province. Here we use methods borrowed from Ecology that allow us to identify if amphora workshops share similar amphoric stamps depending on the spatial distance.

The analysis explores how quantitative approach provides a useful tool for the interpretation of the economic processes. Finally, results pretend to highlight the organization of olive oil production in the Roman Empire linked to the differences observed in the archaeological evidence.

\end{abstract}

\end{frontmatter}

@@

This paper aims to highlight the production dynamics in relation to a specific area within Roman Empire. We want to detect the pattern of olive oil production that link amphora workshops and amphoric stamps.
We focus here on exploring the economic relation between stamps and amphora production centres.

Roman provinces such as Baetica became important production and distribution centers during the Roman Empire. However, it remains under debate how this province was organized and whether it is possible to identify patterns in the olive oil market.

@@

%%\subsection{Jaccard distance}
%The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity by calculating the presence of sets (CITAR). In our case, Jaccard distance was used to compute the mutual presence of traits in the amphora stamps but it does not consider the number of absences. A comparison was done with the distance of the workshops to identify whether there was an association between stamps and spatial distance amongst workshops.

@@

We use the statistical technique Morisita-Horn index. This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity \citep{wolda_similarity_1981}. Morisita-Horn index can be expressed considering 0 as total presence of similarity of stamps and 1 a totally dissimilarity between stamps. In our case, it will be calculated the number of times that one stamp appear in a amphora workshop. This method allows to bear in mind the similar number of times for each repeated stamp per workshop.

@@

%%\subsection{Jaccard distance}

%Result of Jaccard distance can be The coefficients range from x to x.The dendrogram shown in Fig. Bla bla was obtained with the Jaccard distance measure. The dendrogram suggests
